HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
dd

HMEANT shares much of HUME's motivation for providing a
measure that decomposes over semantic units, rather than strings. On the other
hand, there are important differences in design decisions, which we summarize in this
section.

@@

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.

>>>>

HMEANT shares much of HUME's motivation in defining a
measure that decomposes over semantic units, rather than strings. On the other
hand, there are important differences in design decisions, which we summarize in this
section.

@@

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.\oa{we can give some empirical data here.
  In the WMT 13 experiment, Lexi and Barry report a little over 3 mins of annotation
  per sentence + 3 translations. HUME annotation is about 2-4 minutes per sentence.
  UCCA annotation by trained annotators is about 700 tokens/hour (we didn't
  check it for individual sentences), but that's done only once so it should be amortized.}
